\section{Background}
\subsection{Online Advertising}
In the third quarter of 2016, U.S. advertisers invested \$17.6 billion
in digital advertising~\cite{iabq3}. Increasingly, much of this money
is going to mobile advertising; in the first half of 2016, mobile
surpassed search for the first time as the leading ad
format~\cite{iab2016}. In such a massive and diverse industry, the
technology surrounding the online ad ecosystem has grown exceedingly
complex. Online ads can be sourced via premium campaigns, ad networks,
or ad exchanges and involve detailed targeting and accounting
mechanisms~\cite{adscape}. The number of players involved is
constantly increasing, raising the barrier to disrupt the industry
higher than ever ~\cite{lumascape}.

\subsection{Ad-blockers}
The growth of ad-blockers in recent years has been cause for alarm for
many current online advertising stakeholders. In a recent study of 2
million users, Malloy et al. found U.S. ad-blocker penetration to be
15.7-18.6\% (95\% CI)~\cite{malloy}. An active measurement study by
Pujol et al. estimated that 22\% of users were likely using
ad-blockers~\cite{pujol}. Surveys by various entities in the
advertising industry have estimated that 26\% of desktop
users~\cite{iab-blockers} and 37\% of mobile users~\cite{gwi} are
blocking ads in the U.S. Another industry survey estimates that 309
million are using mobile ad-blockers globally (16\% of global
smartphone users)~\cite{pagefair}. A simple back-of-the-envelope
calculation reveals the scale of the impact this has on content
providers: using the most conservative of the above ad-blocker
estimates (15.7\%) and the \$17.6 billion spent in 2016 Q3,
publishers, marketers, and others are missing out on approximately
\$2.8 billion in revenue per quarter due to ad-blocking users. As both
the quantity of money invested into digital advertising and number of
ad-blocking users grow, this figure is becoming increasingly
significant~\cite{iab2016}.

In response to this growth in ad-blocking technology, a new breed of
partnerships are forming. Eyeo GmbH, which makes Adblock Plus
(installed on over 100 million active devices~\cite{abp}), began its
Acceptable Ads program in 2011, which allows “large entities” to pay
in order to have their ads whitelisted for its users. As of 2015, this
list was known to include Google, Microsoft, Amazon, and
Taboola~\cite{whitelist}. Increasingly, the battle over ad-blockers is
being fought in the courtroom. Recently, a German court banned Eyeo
from collecting money from German publishing house Axel
Springer~\cite{axel}. These battles point to the higher-level
rejection of advertisements by users, and suggest that a more
sustainable compensation model is necessary for the long-term internet
to continue to attract users and reward content producers.
