% 3) Overview - similar to the abstract, provide a description of the motivation, challenges, RESEARCH QUESTION (which should be separated from the rest of the text and written in BOLD font), proposed approach (one paragraph) and expected outcomes.

\section{Overview}
Historically, online advertising has served as the primary source of revenue for content creators.
This framework has catalyzed the rapid growth of the internet, as consuming quality content for free is extremely attractive to users.
However, producing such content is not free for publishers who are currently left with two options: sell space on their site to advertisers, or move to a subscription-based model.
Advertisements have largely won this battle, partially due to a few key examples of the “paywall” architecture failing to retain users~\cite{nyt}.
This has led to a modern internet which is filled with publishers entirely reliant on the ads that keep their lights on.

Here, we explore an alternative payment system, Harpocrates, which provides users with a choice to avoid advertisements on the internet and still compensate publishers.
In designing the architecture, we focus on two key factors: convenience and scalability.
The ultimate goal is to minimize the burden on the user by providing a payment system which integrates into the current internet ecosystem, while designing an architecture flexible enough to scale with the internet.
We also describe a proof of concept browser extention, \textit{Un}Acceptable Ads, which allows users to specify the quantity and type of ads that they want to block, offering an immediate compromise between the negatives of ads for users and the need for publishers to be compensated.

Ultimately, the research question explored was: \\
\\
\textbf{Can we devise a scalable internet payment architecture that supports ad-free browsing for users and fair compensation for content publishers?}
